\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{titling}
\setlength{\droptitle}{-10em}   % This is your set screw
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\fontsize{12}{10}\bfseries}{\thesection}{1em}{}
\author{Meeting Agenda}
\title{Mu Alpha Theta}
\date{September 14th, 2023}
\begin{document}
  \maketitle

  \section{Key Points}
    \begin{enumerate}
        \item Join our remind \textbf{@tabbhsmat} for updates and reminders!
        \item Turn in honor policies with signatures to Mrs. Miller or Mrs. White.
        \item To ensure you are in good standing with Mu Alpha Theta, there is a minimum of \textbf{9} hours of tutoring and \textbf{3} Virginia Math League Competitions per academic year.
    \end{enumerate}
  \section{Math Competitions} 
    \begin{itemize}
        \item Upcoming VA Math League Competitions
            \begin{itemize}
                \item October 17th, 2023
                \item November 14th, 2023
            \end{itemize}
            Make sure you sign up to meet member requirements! These competitions are only 30 minutes long and are taken online. 
        \item AMC 8, 10/12A, 10/12B \newline
        Register by \textbf{September 25th, 2023} \newline
        Official Competition Dates are Nov. 8(10/12A), Nov. 14(10/12B), and Jan. 18-24(8)
        
    \end{itemize}
    \section{Upcoming Events for Volunteer Hours}
    \begin{description}
        X-STEM Conference NOVA - October 20th, 2023 (full day) \newline @ Leesburg, VA \newline
        Learn from leading STEM role models, participate in hands-on workshops, and interact with other bright students around the state while learning about a career in STEM and obtain volunteer hours for Mu Alpha Theta or other clubs!
    \end{description}
    \section{STEM Opportunities}
      \begin{enumerate}
          \item NASA's Internship Programs: go to \underline{https://intern.nasa.gov/} for more information
          \item Veritas AI Scholar Program: go to \underline{https://www.veritasai.com/ai-scholars} for more information
      \end{enumerate}
\end{document}