\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{titling}
\setlength{\droptitle}{-10em}   % This is your set screw
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\fontsize{12}{10}\bfseries}{\thesection}{1em}{}
\author{Meeting Agenda}
\title{Mu Alpha Theta}
\date{October 12th, 2023}
\begin{document}
  \maketitle

  \section{Key Points}
    \begin{enumerate}
        \item Join our remind \textbf{@tabbhsmat} for updates and reminders!
        \item Turn in honor policies with signatures to Mrs. Miller or Mrs. White.
        \item To ensure you are in good standing with Mu Alpha Theta, there is a minimum of \textbf{9} hours of tutoring and \textbf{3} Virginia Math League Competitions per academic year.
    \end{enumerate}
  \section{Math Competitions} 
    \begin{itemize}
        \item Upcoming VA Math League Competitions
            \begin{itemize}
                \item October 17th, 2023
                \item November 14th, 2023
            \end{itemize}
            Check Canvas annoucements/email Mr. Martin to get signed up for the VA Math League! 
        \item AMC 8, 10/12A, 10/12B \newline
        Sign up now! \textbf{We have a couple more spots!} \newline
        Official Competition Date is Nov. 14(10/12B).
        \item CNU Regional Math Competition \newline
        February 10th from 8-12:30am @ CNU \newline
        The competition includes individual and team rounds and is a fun experience with friends. Hosted by CNU, students are able to make connections with other bright math students in the area, while obtaining the needed hours for Mu Alpha Theta. 
        
    \end{itemize}
    \section{Upcoming Events}
    \begin{description}
        Mu Alpha Theta New Member Induction - October 19th, 2023 \newline 6:30pm - 7:15pm @ Tabb High School \newline
        Old members can get easy volunteer hours from coming and helping! Volunteers come at 6:15pm. All new members are required to be there. Dress business casual. 
    \end{description}
    \section{STEM Opportunities}
      \begin{enumerate}
          \item NASA's Internship Programs: go to \underline{https://intern.nasa.gov/} for more information
          \item Veritas AI Scholar Program: go to \underline{https://www.veritasai.com/ai-scholars} for more information
      \end{enumerate}
\end{document}