\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{titling}
\setlength{\droptitle}{-10em}   % This is your set screw
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\fontsize{12}{10}\bfseries}{\thesection}{1em}{}
\author{Meeting Agenda}
\title{Mu Alpha Theta}
\date{December 12th, 2023}
\begin{document}
  \maketitle

  \section{Key Points}
    \begin{enumerate}
        \item Join our remind \textbf{@tabbhsmat} for updates and reminders!
        \item Turn in honor policies with signatures to Mrs. Miller or Mrs. White.
        \item To ensure you are in good standing with Mu Alpha Theta, there is a minimum of \textbf{9} hours of tutoring and \textbf{3} Virginia Math League Competitions per academic year.
    \end{enumerate}
  \section{Math Competitions} 
    \begin{itemize}
        \item \textbf{Upcoming VA Math League Competitions} \newline
        These are usually on the second Tuesday of each month and count for one service hour each!
            \begin{itemize}
                \item December 12th, 2023 (TODAY!)
                \item January 16th, 2024
            \end{itemize}
            Check Canvas annoucements/email Mr. Martin to get signed up for the VA Math League! You are given 30 minutes to complete 6 questions online and it is something that you can do anytime throughout the day. 
        \item \textbf{AMC} \newline
        For those that took the AMC 10/12 on November 14th, results will be coming back soon! 
        \item \textbf{CNU Regional Math Competition} \newline
        February 10th, 2024 from 8-12am \newline
        Christopher Newport University \newline
        The competition includes individual and team rounds and is a fun experience with friends.
    \end{itemize}
    
    \section{Upcoming STEM Events and Volunteer Opportunities}
    
    \begin{description}
        \item \textbf{Plant the Moon Challenge} \newline Visit plantthemoon.com for more information!
        \item \textbf{Student Tutors Needed!} \newline 
        Meet Wednesdays after school in Mrs. Griffin's room (119).
    \end{description}
      
\end{document}
